MSD panels 1, 2 and 3 Explant Supernatant

### 2016-09-22 MSD_panels_1_2_3_explant_sup_analysis.Rmd
rechecked data, "missing" in heatmap were actually where we didn't have sup.

#Samples that are "Below Detection Range" means that the signal was "statistically indistinguishable from the background or top of the curve"" and ..."The concentrations calculated are inherently unreliable."

@@

#Plot of all samples and their concentrations
#Note that this includes the samples that manually set to 0.01

@@

```{r get ratio, check NAs, echo=FALSE}

@@

```{r logFC heatmap, check NAs, echo=FALSE}

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = logMockSub24_minus_logMockSub3), color = "white")+
  scale_fill_gradient(low = "green", high = "red")+
  facet_wrap(~Virus)+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")

@@

This is just donors 317,318,323 and 324, which were interesting in the microarray

>>>>

#Samples that are "Below Detection Range" means that the signal was "statistically indistinguishable from the background or top of the curve" and ..."The concentrations calculated are inherently unreliable."

@@

#Plot of all samples and their concentrations
#Note that this includes the samples that manually set to 0.001

@@

```{r get ratio, echo=FALSE}

@@

```{r setup logFC heatmap, echo=FALSE}

#I want the scale to have max intensity a 10-fold change in either direction (log10(10)=1 on my scale and log10(0.1)= -1 on my scale) so I am going to set all values >=1 as 1 and all values <=-1 as -1.

#set all values >=1 as 1

merge24And3 <- merge24And3 %>%
  mutate(max10fold =
           ifelse(
             logMockSub24_minus_logMockSub3 >=1,
         1,
           ifelse(
             logMockSub24_minus_logMockSub3 <=-1,
         -1,logMockSub24_minus_logMockSub3)
           )
  )

@@

```{r logFC heatmap, echo=FALSE}

#Note that we should NOT have data for the following samples  because we didnt have sup for them

# 323-T2-Anything (i.e. no SD90 data)
# Didnt have sup for 326 T1 OR T2 (and this shows T3/T1 so we don't have anything)

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```
This is just donors 317,318,323 and 324, which were interesting in the microarray
